---
title: "Benefits for contributors"
date: last-modified
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include = FALSE, echo = FALSE}
## load packages
packs.html <- c("knitr", "pander", "reporttools", "dplyr", "readxl")
for (i in 1:length(packs.html)){library(packs.html[i], character.only = TRUE)}

knitr::opts_chunk$set(echo = TRUE)

## read in data
path <- getwd()
sci22 <- as.data.frame(read_excel(paste(path, "/data/2023/scicom2023.xlsx", sep = ""), col_types = NULL))
waived <- as.data.frame(read_excel(paste(path, "/data/waived.xlsx", sep = ""), col_types = NULL))

source(paste(path, "/functions/inputData.r", sep = ""))
res <- inputData()
source(paste(path, "/functions/colFmt.r", sep = ""))
```

As a premise note that [EFSPI](https://efspi.org/) is non-profit making and as a principle does not pay an honorarium.

# For participants

The registration fee is waived for participating students and members of regulatory agencies. When registering simply chose the _virtual_ or _face-to-face_ option but do not pay the registration fee.

# For contributors

## Registration waived

For

- contributing academics (incl. students),
- members of the Scientific Program Committee,
- session chairs, presenters, and
- invited panelists

we are able to offer the following benefits, depending on your affiliation:

```{r, include=TRUE, echo=FALSE}
waived[is.na(waived)] <- ""
kable(waived, align = "llccccc")
```

However, if the registration fee is waived for you please still register using `r res["reg_form"]`.

Please book all your travel yourself. For reimbursement please complete [this form](data/2025/20250910_EFSPI_workshop_reimbursement.docx) after the event and send it to `r res["cashiermail"]`.

## Registration fee not waived

Registration fee is *not waived* for, irrespective of institution (industry, regulator, academia):

- poster presenters,
- short topic session presenters.

# Questions?

For feedback and questions send an email to `r res["chairmail"]`.



