---
title: "Past workshops"
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: no
    toc_depth: 2
    toc_float: yes
---

```{r setup, include = FALSE, echo = FALSE}
## load packages
packs.html <- c("knitr", "pander", "reporttools", "dplyr", "readxl")
for (i in 1:length(packs.html)){library(packs.html[i], character.only = TRUE)}

knitr::opts_chunk$set(echo = TRUE)

path <- getwd()
source(paste(path, "/functions/colFmt.r", sep = ""))

## past
path <- getwd()
past <- as.data.frame(read_excel(paste(path, "/data/data.xlsx", sep = ""), col_types = NULL))
past_c <- as.data.frame(read_excel(paste(path, "/data/roster_past.xlsx", sep = ""), col_types = NULL))

ut <- unique(past_c$Type)
ut <- ut[c(4, 2, 3, 1, 7, 6, 5)]
```

# Programs, slidedecks, and recordings

If a recording has been made this can be found on the page with the slidedecks.

`r colFmt("Any views expressed in any of the slidedecks or recordings are personal and do not necessarily represent the speaker's company or organisation's view.")`

```{r programs, include=TRUE, echo=FALSE}
past <- select(past, Year, Program, Slidedecks)
for (i in 2:ncol(past)){past[, i] <- ifelse(past[, i] != "[X](NA)", paste("[X](", past[, i], ")", sep = ""), "")}
past[is.na(past)] <- ""
kable(past, align = "ccc")
```

# Contributors to past workshops: by year

::: {.panel-tabset .nav-pills}

```{r out0, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out1 <- NULL
uy <- unique(past_c$Year)

for (j in 1:length(uy)){
    out1 <- c(out1, knit_expand('tools/pastContributorsYear.qmd'))
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a

a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences0, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```

:::

# Contributors to past workshops: by affiliation

## `r ut[1]`

::: {.panel-tabset .nav-pills}

```{r out1, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out1 <- NULL
dat1 <- filter(past_c, Type == ut[1])
uy <- unique(dat1$Year)
w <- c("Name", "Affiliation")

for (i in 1:length(uy)){
    out1 <- c(out1, knit_expand('tools/pastContributorsType.qmd'))
}
# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a

a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences1, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```

:::

## `r ut[2]`

::: {.panel-tabset .nav-pills}

```{r out2, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out1 <- NULL
dat1 <- filter(past_c, Type == ut[2])
uy <- unique(dat1$Year)

for (i in 1:length(uy)){
    out1 <- c(out1, knit_expand('tools/pastContributorsType.qmd'))
}
# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a

a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences2, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```

:::

## `r ut[3]`

::: {.panel-tabset .nav-pills}

```{r out3, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out1 <- NULL
dat1 <- filter(past_c, Type == ut[3])
uy <- unique(dat1$Year)
w <- "Name"

for (i in 1:length(uy)){
    out1 <- c(out1, knit_expand('tools/pastContributorsType.qmd'))
}
# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a

a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences3, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```

:::

## `r ut[4]`

::: {.panel-tabset .nav-pills}

```{r out4, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out1 <- NULL
dat1 <- filter(past_c, Type == ut[4])
uy <- unique(dat1$Year)
w <- "Name"

for (i in 1:length(uy)){
    out1 <- c(out1, knit_expand('tools/pastContributorsType.qmd'))
}
# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a

a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences4, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```

:::

## `r ut[5]`

::: {.panel-tabset .nav-pills}

```{r out5, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out1 <- NULL
dat1 <- filter(past_c, Type == ut[5])
uy <- unique(dat1$Year)
w <- "Name"

for (i in 1:length(uy)){
    out1 <- c(out1, knit_expand('tools/pastContributorsType.qmd'))
}
# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a

a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences5, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```

:::

## `r ut[6]`

::: {.panel-tabset .nav-pills}

```{r out6, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out1 <- NULL
dat1 <- filter(past_c, Type == ut[6])
uy <- unique(dat1$Year)
w <- c("Name", "Affiliation")

for (i in 1:length(uy)){
    out1 <- c(out1, knit_expand('tools/pastContributorsType.qmd'))
}
# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a

a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences6, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```

:::

## `r ut[7]`

::: {.panel-tabset .nav-pills}

```{r out7, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out1 <- NULL
dat1 <- filter(past_c, Type == ut[7])
uy <- unique(dat1$Year)
w <- c("Name", "Affiliation")

for (i in 1:length(uy)){
    out1 <- c(out1, knit_expand('tools/pastContributorsType.qmd'))
}
# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a

a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences7, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```

:::
