---
title: "Scientific Committee"
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include = FALSE, echo = FALSE}
## load packages
library("knitr")
library("pander")
library("reporttools")
library("dplyr")
library("readxl")

knitr::opts_chunk$set(echo = TRUE)

```

# How to get on the scientific committee

Principles for joining the Scientific Committee have been outlined by EFSPI workshop leadership in this [slidedeck](data/EFSPI_Workshop_Principles_SciCom.pdf).

# Members

::: {.panel-tabset .nav-pills}

# 2026

In 2026 the members of the scientific committee are (for regulators countries in parentheses):

```{r, include=TRUE, echo=FALSE}
kable(select(filter(sci26, LET == 0), First, Last, Gender, Type, Affiliation), align = "llccl", col.names = c("First", "Last", "Gender", "Type", "Affiliation"))
```

# 2025

In 2025 the members of the scientific committee are (for regulators countries in parentheses):

```{r, include=TRUE, echo=FALSE}
kable(select(sci25, First, Last, Gender, Type, Affiliation), align = "llccl", col.names = c("First", "Last", "Gender", "Type", "Affiliation"))
```

# 2024

In 2024 the members of the scientific committee were (for regulators countries in parentheses):

```{r, include=TRUE, echo=FALSE}
kable(select(sci24, First, Last, Gender, Type, Affiliation), align = "llccl", col.names = c("First", "Last", "Gender", "Type", "Affiliation"))
```

In 2024 we also had a committee that contributed to the planning of HTA talks.

```{r, include=TRUE, echo=FALSE}
kable(select(hta24, First, Last, Gender, Type, Affiliation), align = "llccl", col.names = c("First", "Last", "Gender", "Type", "Affiliation"))
```

# 2023

In 2023 the members of the scientific committee were (for regulators countries in parentheses):

```{r, include=TRUE, echo=FALSE}
kable(select(sci23, -Local, -SciCom, -email), align = "llccl")
```

# 2022

In 2022 the members of the scientific committee were:

```{r, include=TRUE, echo=FALSE}
kable(select(sci22, -Local, -SciCom, -email), align = "llccl")
```

See also the `r paste("[program of ", 2022, "](", past[past[, "Year"] == 2022, "Program"], ")", sep = "")`.

:::

# Questions?

For feedback and questions send an email to `r res["chairmail"]`.



